---
title: "Data Quality Checks: Inequalities"
subtitle: "Report looks for errors in files intended for deprivation tab of ScotPHO profiles tool"
output: html_document
runtime: shiny

---

```{r setup, include=FALSE}
#global options for markdown report
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}

data_folder <- "/PHI_conf/ScotPHO/Profiles/Data/"

#read in geography code names dictionary
code_dictionary <-readRDS(paste0(data_folder,"Lookups/Geography/codedictionary.rds")) 

#Read in indicator file being checked (switch file path if working on test in
profiles_data_folder <- "/PHI_conf/ScotPHO/Profiles/Data"
output_folder <- if(test_file){
    file.path(profiles_data_folder, "Test Shiny Data") # for newly developed indicators that have never been in the profiles tool
    } else {
      file.path(profiles_data_folder, "Data to be checked") # for established indicators already in the profiles tool 
    }
  
#Read in indicator file being checked
data_indicator <- readRDS(paste0(output_folder,"/", filename, "_ineq.rds")) %>%
  mutate(geo_type=substr(code,1,3)) #add field identifying geography type

#Add geography code names
data_indicator <- left_join(x=data_indicator, y=code_dictionary, by="code") %>%
mutate(code_name=paste0(code,": ",as.character(areaname))) #add field with geography code & name
  
#Test which optional geographies are present in dataset 
scot_quintiles <-  any(substr(data_indicator$code,1,3) =="S00")
hb_quintiles  <- any(substr(data_indicator$code,1,3) == "S08")
ca_quintiles <- any(substr(data_indicator$code,1,3) == "S12")


## Are the deprivation data grouped by sex? If so this needs to be accounted for in the QA
sex_column <- "sex" %in% names(data_indicator) # gives TRUE or FALSE
# defining a new column (sex) to be added if it's not present in the data already:
library(tibble) # for adding a column here
cols <- c(sex = "Total")
data_indicator <- data_indicator  %>%
  add_column(!!!cols[!names(cols) %in% names(.)]) # adds a sex column, and fills it with "Total" if it doesn't exist in the data

#Read in old indicator data file from network /Shiny data folder - if one exists (new indicators won't have a historic file)
old_indicator_filepath <- paste0(data_folder, "Shiny Data/", filename, "_ineq.rds") #create value which is file path to old file

# statement that checks if there an old indicator data file of the same name exists in Shiny data folder 
if(file.exists(old_indicator_filepath)) {
  skip_historic_file_checks <-"n" # if historic file found then instruct this report not to skip over thse checks
  old_data_indicator <- readRDS(paste0(data_folder, "Shiny Data/", filename, "_ineq.rds")) #read in file if one exists
} else {
  skip_historic_file_checks <-"y" #if no historic file found then instruct this report to skip over some of the checks
  old_indicator_filepath <-"No historic file available for comparison. Check filename spelling or 'shiny data' network folder if you were expecting a comparison" #if no historic file exists set value to no file available
}


# Pre-defined geographies that will be used in 'Check 3' comparing old & new file 
# check_extras is an optional parameter that can be used to supply additional bespoke geography codes to check
# check_codes <- c("S00000001","S08000031","S12000036",check_extras) 
```

Indicator:  **`r filename`** <br>
Date:  **`r format(Sys.time(), '%d %B, %Y %H:%M')`** <br>

**New** indicator file:  /`r (paste0(output_folder,"/", filename, ".rds"))`<br>
**Old** indicator file (for comparisons):  /`r (paste0(old_indicator_filepath))` <br>

------------------------------------------------------------------------------------

**Geographies present in indicator output file** <br>
NHS board: `r hb_quintiles` <br>
Council area: `r ca_quintiles` <br>
Scotland: `r scot_quintiles` <br>

------------------------------------------------------------------------------------

##**Data check 1:** <br>
##Expected Geographies

```{r include=FALSE}
#Code chunk for counting unique geographies & quintiles appear for each of the quintile types
#Within Scotland Quintiles - all geo types (Scotland, NHS Board and local authority) could be present but not necessarily all quintiles (e.g., Shetland, Orkney)
# Within HB Quintiles - expect 14 nhs boards only, all quintiles (5 quintils + total=6) should be available
# Within LA Quintiles - expect 32 la only, all quintiles should be available
#df counts how many distinct quintiles for each geography by quint type, areaname and year - used in checks on quintiles present
quintile_checks <- data_indicator %>%
  group_by(quint_type, trend_axis, code, areaname, geo_type, year, sex) %>%
  summarise(count_q=n()) %>%
  ungroup()
#df counts how many distinct geographies by quint type and year - used to check which geographies are present
geo_checks <- quintile_checks %>%
  group_by(quint_type, geo_type, trend_axis,sex) %>%
  summarise(count=n()) %>%
  spread(geo_type, count) %>%
  ungroup()

#flextable to check how many geogrpahy types are present each year for within scotland quintiles
ft_sc_quin_check <- geo_checks %>%
  subset(quint_type=="sc_quin") %>%
  flextable() %>%
  color(~ S00!=1, ~S00, color = "red") 

if(hb_quintiles == TRUE) {ft_sc_quin_check<- ft_sc_quin_check %>%  color(~ S08!=14, ~S08, color = "red")} # Should be 14 NHS boards
if(ca_quintiles == TRUE) {ft_sc_quin_check<- ft_sc_quin_check %>%  color(~ S12!=32, ~S08, color = "red")} # Should be 32 council areas

ft_sc_quin_check<- ft_sc_quin_check %>%
  autofit()

if(hb_quintiles == TRUE){
# flextable on hb quintiles - summary table of years and geogrpahy types present
ft_hb_quin_check <- geo_checks %>%
  subset(quint_type=="hb_quin") %>%
  flextable() %>%
  color(~ !is.na(S00), ~S00, color = "red") %>% # Should be no records for scotland code
  color(~ S08!=14, ~S08, color = "red") %>% # Expect 14 NHS boards for board quintiles
  color(~ !is.na(S12), ~S12, color = "red") %>% # Should be no records for council codes
  autofit()}

if(ca_quintiles == TRUE){
# flextable on hb quintiles - summary table of years and geogrpahy types present
ft_ca_quin_check <- geo_checks %>%
  subset(quint_type=="ca_quin") %>%
  flextable() %>%
  color(~ !is.na(S00), ~S00, color = "red") %>% # Should be no records for scotland code
  color(~ S12!=32, ~S12, color = "red") %>% # Expect 32 council areas for CA quintiles
  color(~ !is.na(S08), ~S08, color = "red") %>% # Should be no records for HB codes
  autofit()
}

```

### Within Scotland deprivation quintiles
Within Scotland quintiles should return data for Scotland, and may also be available for HBs and CAs.<br>
Table below indicates which type & how many geography codes are present & highlights if this is unexpected count

```{r}
#print flextable
ft_sc_quin_check 
```

### Within health board or council deprivation quintiles
If present, within hb/ca quintiles should only return data for either nhs board or councils.<br>
Conditional formatting will show up if distinct geography counts are not as expected 
```{r}

if(hb_quintiles==TRUE){
ft_hb_quin_check #print flextable
} else {
paste0("No health board quintile present")
}   

if(ca_quintiles==TRUE){
ft_ca_quin_check #print flextable
} else {
paste0("No within council quintile present")
}   


```

------------------------------------------------------------------------------------  

##Data check 2: Expected deprivation quintiles 
#This section checks that all geographies that have deprivation data have the full complement of quintiles (i.e., data for 5 quintiles + a total = 6 rows). If there are any gaps these will be #highlighted in the table.
###Within Health Board/Council Quintiles
```{r}

# # if ca or hb quintile sum not equal to 6 theres an issue (since within geography deprivation should always have 5 quintiles plus a total)
# hbca_quintile_warning <- quintile_checks %>%
#   mutate(q_count= ifelse(quint_type!="sc_quin" && count_q!=6, TRUE, FALSE)) %>%
#   summarise(quint_error_total=sum(q_count,na.rm=TRUE))
# #Text output when ca or hb quintiles not correct
# ifelse(hbca_quintile_warning $quint_error_total == 0, "Within CA and HB quintiles all appear present",
# "STOP AND CHECK....looks like not all geographies have correct number of quintiles for within CA or HB quintiles")

# function to check which areas are missing one or more of the specified quintile types, by areatype
prep_areatype_quintile_check <- function (areatype) {
  
  if (areatype=="Scotland") {
    qtype <- "sc_quin"
    warning <- sc_quintile_warning
  } else if (areatype=="HB") {
    qtype <- "hb_quin"
    warning <- hb_quintile_warning
  } else if (areatype=="CA") {
    qtype <- "ca_quin"
    warning <- ca_quintile_warning
  }
  
  if (warning$quint_error_total != 0) { # if gaps found
    areatype_quintile_check <- data_indicator %>%
      subset(quint_type==qtype) %>%
      mutate(q=paste0("Q",as.character(quintile))) %>%
      group_by(trend_axis, areaname, code, geo_type, q, sex) %>%
      summarise(count=n())%>%
      spread(q, count) %>%
      mutate(qsum=sum(Q1,Q2,Q3,Q4,Q5,QTotal, na.rm=TRUE)) %>%
      ungroup() %>%
      subset(qsum<6) %>%
      arrange(geo_type,code, trend_axis) %>%
      select(geo_type, areaname, code, trend_axis, everything()) %>%
      flextable() %>%
      bg(i= ~Q5==1, j= ~Q5, bg="red") %>%
      merge_v(j=c("areaname","code","geo_type")) %>%
      autofit() %>%
      theme_vanilla()
    
    areatype_quintile_check
    } else {
        "No table needed: no gaps to show."
      }
}
# Quintile checks if hb_quin quintiles are in the data:
if (hb_quintiles) {
  # if hb quintile sum not equal to 6 there's an issue (since within geography deprivation should always have 5 quintiles plus a total)
  hb_quintile_warning <- quintile_checks %>%
    mutate(q_count = ifelse(quint_type=="hb_quin" && count_q!=6, TRUE, FALSE)) %>%
    summarise(quint_error_total=sum(q_count,na.rm=TRUE))
  #Text output when hb quintiles not correct
  ifelse(hb_quintile_warning$quint_error_total == 0, "There are no gaps in the HB-level quintile data. :-)",
  "STOP AND CHECK....looks like not all geographies have correct number of HB-level quintiles.")
prep_areatype_quintile_check("HB")
}
# Quintile checks if ca_quin quintiles are in the data:
if (ca_quintiles) {
  # if ca quintile sum not equal to 6 there's an issue (since within geography deprivation should always have 5 quintiles plus a total)
  ca_quintile_warning <- quintile_checks %>%
    mutate(q_count = ifelse(quint_type=="ca_quin" && count_q!=6, TRUE, FALSE)) %>%
    summarise(quint_error_total=sum(q_count,na.rm=TRUE))
  #Text output when ca quintiles not correct
  ifelse(ca_quintile_warning$quint_error_total == 0, "There are no gaps in the CA-level quintile data. :-)",
  "STOP AND CHECK....looks like not all geographies have correct number of CA-level quintiles.")
prep_areatype_quintile_check("CA")
}
# Message if no ca/hb quintiles are in the data:
if(hb_quintiles==FALSE & ca_quintiles==FALSE) {
  "There are no HB- or CA-level quintiles in the data."
}



```

###Within Scotland quintiles"
```{r}
sc_quintile_warning <- quintile_checks %>%
  subset(quint_type=="sc_quin") %>%
  mutate(q_count= ifelse(count_q!=6, TRUE, FALSE)) %>%
  summarise(quint_error_total=sum(q_count,na.rm=TRUE))

#Text output when one or more Scotland-wide quintile is missing from a geography represented in these data:
prep_areatype_quintile_check("Scotland")


# #Text output when one or more sc quintile is missing from an NHS Board of Council Area
#  ifelse(sc_quintile_warning $quint_error_total == 0, "No geographies are missing a Scotland quintile",
#  paste0("STOP and check table below!...There are ", sc_quintile_warning$quint_error_total[1]," geography/time periods where not all Scotland quintiles are present.  This is most likely in small areas eg Island regions.  If many regions are affected then indicator may not be suitable for publication."))       
# # df to checkk how many areas are missing one or more scottish quintiles
# sc_quintile_check <- data_indicator %>%
#   subset(quint_type=="sc_quin") %>%
#   mutate(q=paste0("Q",as.character(quintile))) %>%
#   group_by(trend_axis, areaname, code,geo_type, q) %>%
#   summarise(count=n())%>%
#   spread(q, count) %>%
#   mutate(qsum=sum(Q1,Q2,Q3,Q4,Q5,QTotal, na.rm=TRUE)) %>%
#   ungroup() %>%
#   subset(qsum<6) %>%
#   arrange(geo_type,code, trend_axis)
# # Flextable displying which geographies and years do not ahave all scotland quintiles represented
# ft_sc_quintile_check <- sc_quintile_check %>%
#   select(geo_type, areaname, code,trend_axis, Q1:qsum) %>%
#   flextable() %>%
#   bg(i= ~Q5==1, j= ~Q5, bg="red") %>%
#   merge_v(j=c("areaname","code","geo_type")) %>%
#   autofit() %>%
#   theme_vanilla()
# ft_sc_quintile_check
```

------------------------------------------------------------------------------------  
<!-- HISTORICAL DATA CHECKS NEEDS WORK  -->

<!-- ##Data check 3: Compare previous file  -->
<!-- The table below compares the numerator, measure and CI of the latest file against the last shiny data file prepared.<br> -->
<!-- Conditional formatting will highlight when figures do not match, tolerance is to 3 decimal places <br> -->
<!-- Sometimes figures can change, e.g when the SMR records are more complete or new references files like the postcode lookups have been used.<br> -->
<!-- Use your judgement to decide if any differences are within acceptable range. -->

<!-- ```{r} -->
<!-- if(new_ind==FALSE){ -->
<!-- new_file <- data_indicator %>% subset(code %in% check_codes) -->
<!-- old_file <- old_data_indicator %>% subset(code %in% check_codes)%>% -->
<!--   select (code, year, quint_type,quintile, numerator, rate:rel_range) -->
<!-- #checks below only for matching rates/inequality estimates, not looking at CIs? -->
<!-- matched <- merge(x = new_file, y = old_file, by=c("code", "year","quint_type", "quintile")) %>% -->
<!--   mutate(rate_match = round((rate.x-rate.y)/rate.x,3), -->
<!--          sii_match = round((sii.x-sii.y)/sii.x,3), -->
<!--          rii_match = round((rii.x-rii.y)/rii.x,3), -->
<!--          par_match = round((par.x-par.y)/par.x,3), -->
<!--          year=as.factor(year), -->
<!--          sum_matches=sum(rate_match, sii_match, rii_match, par_match, na.rm=TRUE)) %>% -->
<!--   subset(sum_matches!=0) -->
<!-- if (nrow(matched) == 0) {"Old and new data files values match" -->
<!-- } else{ flextable(matched, -->
<!--   col_keys = c("code", "areaname","year","numerator.x", "numerator.y","numerator_match", -->
<!--                "rate.x", "rate.y","rate_match", -->
<!--                "sii.x","sii.y", "sii_match", -->
<!--                "rii.x","rii.y", "rii_match", -->
<!--                "par.x","par.y", "par_match")) %>% -->
<!--   set_header_labels(numerator.x="numerator_new", -->
<!--                     numerator.y="numerator_old", -->
<!--                     rate.x ="rate_new", -->
<!--                     rate.y="rate_old", -->
<!--                     sii.x="lowci_new", -->
<!--                     sii.y="lowci_old", -->
<!--                     rii.x="upci_new", -->
<!--                     rii.y="upci_old", -->
<!--                     par.x="upci_new", -->
<!--                     par.y="upci_old") %>% -->
<!--   autofit()} -->
<!-- }else if(new_ind==TRUE){ -->
<!--   "New_ind parameter set to TRUE - no historic checks run" -->
<!-- } -->
<!-- ``` -->

---------------------------------------------------------------------------------

##Data check 4:
####Rates within Confidence intervals
Do any rates fall outwith the confidence limits - they shouldn't!?
This stage checks the CIs for the rate, the SII and the RII.

```{r, echo=FALSE}
# Check no rates/percentages sit outside of CI range  
 confidence_check <- data_indicator %>% 
  mutate(ci_error = ifelse(rate<lowci | rate>upci, TRUE, FALSE),
         sii_ci_error = ifelse(sii<lowci_sii | sii>upci_sii, TRUE, FALSE),
         rii_ci_error = ifelse(rii<lowci_rii | rii>upci_rii, TRUE, FALSE)) %>%
  summarise(ci_error_total = sum(ci_error,sii_ci_error,rii_ci_error, na.rm = TRUE))
ifelse(confidence_check$ci_error_total == 0, "No rates outwith confidence limits :-)",
"Uh-oh looks like there are some rates outwith confidence limits :(")
```

---------------------------------------------------------------------------------

##Data check 5:
#### Small numbers
Look at proportion of areas and quintiles where more than 10% of row include counts of less than 5 and therefore may not be robust. 

```{r}
small_count_data <- data_indicator  %>% 
  group_by(geo_type, quint_type, quintile, year,sex) %>%
  summarise(count=n(),u5=sum(numerator<5)) %>%
  mutate(percent_U5=u5/count*100,
         year =as.factor(year)) %>%
  ungroup() %>%
  subset(percent_U5>10)

if(nrow(small_count_data)>0) {flextable(small_count_data)} else {"No counts less than 5."}


```

-------------------------------------------------------------------------------

<!-- ##Data check 6:-->
<!-- #### Check if there is a linear relationship across deprivation quintiles-->
<!-- This is a quick way to summarise if relationship with deprivation is clearly linear or not. If the relationship is--> <!-- <!-- obviously not linear then question whether measures such as SII and RII are helpful? -->

<!-- ```{r} -->
<!-- # look at which geographies codes/types have linear or non-linear patterns across deprivation quintiles  -->
<!-- linear_trends <- data_indicator  %>% -->
<!--   select(code, year, rate, quint_type, quintile, geo_type) %>% -->
<!--   subset(quintile != "Total") %>% -->
<!--   mutate(quintile=paste0("Q",quintile)) %>% -->
<!--   group_by(code, year, quint_type) %>% -->
<!--   spread(quintile, rate) %>% -->
<!--   mutate(pattern=case_when((Q1>Q2 & Q2>Q3 & Q3>Q4 & Q4>Q5)~"descending",(Q1<Q2 & Q2<Q3 & Q3<Q4 & Q4<Q5) ~"ascending", TRUE~"non_linear")) %>% -->
<!--   group_by(geo_type, quint_type, year, pattern) %>% -->
<!--   summarise(count=n()) %>% -->
<!--   group_by(geo_type, quint_type,year) %>% -->
<!--   mutate(sum=sum(count)) %>% -->
<!--   pivot_wider(names_from = pattern, values_from = count,values_fill=list(count=0)) %>% -->
<!--   mutate(percent_linear=100-round(non_linear/sum*100,1)) -->
<!-- ft <- linear_trends %>% -->
<!--  #select(geo_type,quint_type,year,ascending, descending, non_linear,sum,percent_linear) %>% -->
<!-- select_if(names(.) %in% c('geo_type','quint_type','year','ascending', 'descending','non_linear','sum','percent_linear')) %>% -->
<!--   flextable() %>% -->
<!--   merge_v(j=c("geo_type","quint_type")) %>% -->
<!--   autofit()%>% -->
<!--   theme_vanilla() -->
<!-- ft -->
<!-- ``` -->

-------------------------------------------------------------------------------
##Data check 7: Shiny app

```{r}
shinyApp(
  ui = fluidPage(
     fluidRow(
      fluidRow(column(12,(p("Use dropdowns to adjust charts - remember geography code selected needs to match the quintile type")))),
      column(5,selectInput("code_selected", "Area:", choices = unique(data_indicator$code_name),multiple = FALSE, selected="S00000001: Scotland")),
     column(3,selectInput("quint_selected", "Quintile:", choices = unique(data_indicator$quint_type),multiple = FALSE, selected="sc_quin")),
     column(3,selectInput("year_selected", "Year:", choices = unique(data_indicator$year),multiple = FALSE,selected=max(data_indicator$year))),
     column(3,selectInput("sex_selected", "Sex:", choices = unique(data_indicator$sex),multiple = FALSE,selected="Total"))),
     fluidRow(column(8,(h3("Check annual rates by quintile and rate trends")))),
     fluidRow(
       column(6,plotlyOutput("rate_bar")),
       column(6,plotlyOutput("rate_trend"))),
     fluidRow(column(8,(h3("Check SII and RII trends")))),
     fluidRow(
       column(6,plotlyOutput("sii_trend")),
       column(6,plotlyOutput("rii_trend"))),
     fluidRow(column(8,(h3("Check PAR")))),
     fluidRow(
       column(6,plotlyOutput("par_bar")),
       column(6,plotlyOutput("par_trend")))
    ),
  
  
  server = function(input, output) {
    
    #reactive simd trend data
    simd_trend_data<- reactive({
    rate_data <- data_indicator %>% # reactive dataset for trend chart
    select(code,code_name, year, sex, numerator, denominator, rate, quint_type, quintile, geo_type, par, rii, sii) %>%
    subset(quint_type==input$quint_selected & code_name==input$code_selected & sex == input$sex_selected) %>%
    arrange(quintile) %>% #this is needed to make palette assignments work well
    droplevels()
    })
    
    #reactive simd data single year
    simd_singleyr_data<- reactive({
    bar_rate_data <- simd_trend_data() %>% # reactive dataset for bar chart
    subset(year==input$year_selected & sex == input$sex_selected) %>%
    mutate(average=rate[quintile=="Total"]) %>%
    filter(quintile !="Total") %>%
    droplevels()
    })
    
    # RATE-BAR CHART
    output$rate_bar <- renderPlotly({
    
    pal_rate_bar <- case_when(   simd_singleyr_data()$quintile == "1" ~ '#022031', #Palette for plot 
                                 simd_singleyr_data()$quintile == "2" ~ '#313695', 
                                 simd_singleyr_data()$quintile == "3" ~ '#4575b4', 
                                 simd_singleyr_data()$quintile == "4" ~ '#74add1', 
                                 simd_singleyr_data()$quintile == "5" ~ '#abd9e9')
    rate_bar <- plot_ly(data=   simd_singleyr_data(), x=~quintile) %>%
      #comparator line
     add_trace(y = ~average, name = "Average", type = 'scatter', mode = 'lines',
              line = list(color = '#FF0000'), hoverinfo="skip") %>%
      #quintile bars   
     add_bars(y = ~rate, color = ~ quintile, marker = list(color = pal_rate_bar))  %>%
      layout(title=paste0("Year: ",input$year_selected),bargap = 0.1, margin=list(b = 140),
             showlegend = FALSE) %>%
      config(displayModeBar = F, displaylogo = F, editable =F) # taking out toolbar
    })
    
    # RATE-LINE CHART
    output$rate_trend <- renderPlotly({
    
    #Palette for trend plot
    pal_simd_trend <- case_when(simd_trend_data()$quintile == "1" ~ '#022031',
                                    simd_trend_data()$quintile == "2" ~ '#313695',
                                    simd_trend_data()$quintile == "3" ~ '#4575b4',
                                    simd_trend_data()$quintile == "4" ~ '#74add1',
                                    simd_trend_data()$quintile == "5" ~ '#abd9e9',
                                    simd_trend_data()$quintile == "Total" ~ '#FF0000')
    tooltiptext_trend <- c(paste0(simd_trend_data()$year, ": ", simd_trend_data()$rate))
    
    #Create trend plot
    rate_trend <- plot_ly(data= simd_trend_data(), x=~year,hoverinfo="text") %>%
      add_lines(y = ~rate, name = ~quintile, type = 'scatter',text = tooltiptext_trend,
                mode = 'lines', color = ~quintile,  colors = pal_simd_trend) %>%
              layout(yaxis = list(rangemode = "tozero")) # force yaxis to start at zero
    })
    
    # SII
    output$sii_trend <- renderPlotly({
      
    index_data <- simd_trend_data()  %>%  filter((quintile == "Total"))
    tooltiptext_sii <- c(paste0(index_data$year, ": ", index_data$sii))
    
    sii_trend <-plot_ly(data=index_data, x=~year, hoverinfo="text") %>%
          add_lines(y = ~sii, name = "Absolute inequality (SII)", type = 'scatter', 
                    text = tooltiptext_sii, mode = 'lines',
                    line = list(color = '#74add1'))  %>%
        layout(yaxis = list(rangemode = "tozero")) %>% # force yaxis to start at zero
          config(displayModeBar = FALSE, displaylogo = F,  editable =F) # taking out toolbar
    })
    
    #RII
    output$rii_trend <- renderPlotly({
    index_data <- simd_trend_data()  %>%  filter((quintile == "Total"))
    tooltiptext_rii <- c(paste0(index_data$year, ": ", index_data$rii))
    
    plot_ly(data=index_data, x=~year,hoverinfo="text") %>%
          add_lines(y = ~rii, name = "Relative gap", type = 'scatter',
                    text = tooltiptext_rii, mode = 'lines',line = list(color = '#313695')) %>%
              layout(yaxis = list(rangemode = "tozero")) %>% # force yaxis to start at zero
          config(displayModeBar = FALSE, displaylogo = F, editable =F) # taking out toolbar
    
    })
    
    
  #PAR Barchart
  output$par_bar <- renderPlotly({
    
  par_bar_data <- simd_singleyr_data() %>% 
       mutate(baseline = rate[quintile == "5"],
       diff_baseline = rate - rate[quintile == "5"]) %>% 
       droplevels()  
  plot_ly(data = par_bar_data, x = ~quintile,hoverinfo="text") %>%
      add_bars(y = ~baseline, name= "", marker = list(color = "#4da6ff"), showlegend = FALSE) %>%
      add_bars(y = ~diff_baseline, name = "Attributable to deprivation",
               marker = list(color = "#ffa64d"), showlegend = FALSE) %>%
      layout(title=paste0("Year: ",input$year_selected),
        bargap = 0.1, barmode = 'stack', showlegend = T,
             legend = list(x = 0.9, y = 0.9),
             margin = list(b = 140)) %>%
      config(displayModeBar = FALSE, displaylogo = F, editable =F) # taking out toolbar
  })
    #Par Trends  
output$par_trend <- renderPlotly({
  
  #preparing data needed
  simd_partrend_data <- simd_trend_data() %>%
    subset(quintile == "Total") %>% 
    droplevels()
  
  par_trend_plot <- plot_ly(data=simd_partrend_data, x=~year,
                              hoverinfo="text") %>%
      add_lines(y = ~par, type = 'scatter', mode = 'lines', line = list(color = "#4575b4")) %>%
      layout(margin = list(b = 140),
            yaxis = list(rangemode = "tozero")) %>% # force yaxis to start at zero) %>% #to avoid labels getting cut out
      config(displayModeBar = FALSE, displaylogo = F, editable =F) # taking out toolbar
    })
  
  
  
    },# server close
  options = list(height = 2000)
)
```

```{r, echo=FALSE}
# stop running shiny when close QA report
onStop(function() {
  stopApp()
})
```
