---
title: "Data Quality Checks: Inequalities"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
##global options for markdown report
# echo false suppresses code in final report unless otherwise stated
knitr::opts_chunk$set(echo = FALSE)
```


```{r, include=FALSE}
#read in geography code names dictionary
code_dictionary <- readRDS(paste0(data_folder,"Lookups/Geography/codedictionary.rds")) 
#Read in indicator file being checked
data_indicator <- readRDS(paste0(data_folder, "Data to be checked/", filename, "_ineq.rds")) %>%
  mutate(geo_type=substr(code,1,3))
#Add geography code names
data_indicator <- left_join(x=data_indicator, y=code_dictionary, by="code") %>%
mutate(code_name=paste0(code,": ",as.character(areaname))) #add field with geography code & name
  
#Test which optional geographies are present in dataset 
scot <-  any(substr(data_indicator$code,1,3) =="S00")
board <- any(substr(data_indicator$code,1,3) == "S08")
ca <- any(substr(data_indicator$code,1,3) == "S12")
#Optional parameters allows for checking against previously run data file.
#Paramater also handles if old indicator name to be different to current name.
if (new_ind==FALSE){ #if qa is true then open old indicator file for comparisons
    if (old_file == "default"){  #if no old_filename supplied default to new filename supplied
            old_filename <- {{filename}}
    }else if (old_file != "default"){
            old_filename <- {{old_file}}} #Reading last shiny data file loaded for comparisons.
old_data_indicator <- readRDS(paste0(data_folder, "Shiny Data/", old_filename, "_ineq.rds"))
}else if(new_ind==TRUE){
  old_filename <- "no historic file"
}
# Pre-defined geographies that will be used in 'Check 3' comparing old & new file 
# check_extras is an optional parameter that can be used to supply additional bespoke geography codes to check
check_codes <- c("S00000001","S08000031","S12000036",check_extras) 
```

Indicator:  **`r filename`** <br>
Date:  **`r format(Sys.time(), '%d %B, %Y %H:%M')`** <br>

**New** indicator file:  /`r (paste0(data_folder, "Data to be checked/", filename, ".rds"))`<br>
**Old** indicator file (for comparisons):  /`r if(new_ind==FALSE){(paste0(data_folder, "Shiny Data/", old_filename, ".rds"))}`

------------------------------------------------------------------------------------

**Geographies present in dataset** <br>
NHS board: `r board` <br>
Council area: `r ca` <br>
Scotland: `r scot` <br>

------------------------------------------------------------------------------------

##Data check 1: Expected Geographies

```{r include=FALSE}
#Code chunk for counting unique geographies & quintiles appear for each of the quintile types
#Within Scotland Quintiles - all geo types (Scotland, NHS Board and local authority) should be present but not necessarily all quintiles
# Within HB Quintiles - expect 14 nhs boards only, all quintiles (5 quintils + total=6) should be available
# Within LA Quintiles - expect 32 la only, all quintiles should be available
#df counts how many distinct quintiles for each geography by quint type, areaname and year - used in checks on quintiles present
quintile_checks <- data_indicator %>%
  group_by(quint_type, trend_axis, code, areaname, geo_type, year) %>%
  summarise(count_q=n()) %>%
  ungroup()
#df counts how many distinct geographies by quint type and year - used to check which geographies are present
geo_checks <- quintile_checks %>%
  group_by(quint_type, geo_type, trend_axis) %>%
  summarise(count=n()) %>%
  spread(geo_type, count) %>%
  ungroup()
#flextable to check how many geogrpahy types are present each year for within scotland quintiles
ft_sc_quin_check <- geo_checks %>%
  subset(quint_type=="sc_quin") %>%
  flextable() %>%
  color(~ S00!=1, ~S00, color = "red") %>% # Should be 14 NHS boards
  color(~ S08!=14, ~S08, color = "red") %>% # Should be 14 NHS boards
  color(~ S12!=32, ~S08, color = "red") %>%# Should be 14 NHS boards
  autofit()
# flextable on hb quintiles - summary table of years and geogrpahy types present
ft_hb_quin_check <- geo_checks %>%
  subset(quint_type=="hb_quin") %>%
  flextable() %>%
  color(~ !is.na(S00), ~S00, color = "red") %>% # Should be no records for scotland code
  color(~ S08!=14, ~S08, color = "red") %>% # Expect 14 NHS boards for board quintiles
  color(~ !is.na(S12), ~S12, color = "red") %>% # Should be no records for council codes
  autofit()
# flextable on hb quintiles - summary table of years and geogrpahy types present
ft_ca_quin_check <- geo_checks %>%
  subset(quint_type=="ca_quin") %>%
  flextable() %>%
  color(~ !is.na(S00), ~S00, color = "red") %>% # Should be no records for scotland code
  color(~ S12!=32, ~S12, color = "red") %>% # Expect 14 NHS boards for board quintiles
  color(~ !is.na(S08), ~S08, color = "red") %>% # Should be no records for council codes
  autofit()
```

### Within Scotland deprivation quintiles
Within Scotland quintiles should return data for scotland, nhs board and councils.<br>
Table below indicates which type & how many geography codes are present & highlights if this is unexpected count

```{r}
#print flextable
ft_sc_quin_check 
```

### Within health board or council deprivation quintiles
Within hb/ca quintiles should only return data for either nhs board or councils.<br>
Conditional formatting will show up if distinct geography counts are not as expected 
```{r}
#print flextable
ft_hb_quin_check 
ft_ca_quin_check
```

------------------------------------------------------------------------------------  

##Data check 2: Expected deprivation quintiles 
###Within Health Board/Council Quintiles
```{r}
# if ca or hb quintile sum not equal to 6 theres an issue (since within geography deprivation shold always have 5 quintiles plus a total)
hbca_quintile_warning <- quintile_checks %>%
  mutate(q_count= ifelse(quint_type!="sc_quin" && count_q!=6, TRUE, FALSE)) %>%
  summarise(quint_error_total=sum(q_count,na.rm=TRUE))
#Text output when ca or hb quintiles not correct
ifelse(hbca_quintile_warning $quint_error_total == 0, "Within CA and HB quintiles all appear present :-)",
"STOP AND CHECK....looks like not all geographies have correct number of quintiles for within CA or HB quintiles")
```

###Within Scotland quintiles"
```{r}
sc_quintile_warning <- quintile_checks %>%
  subset(quint_type=="sc_quin") %>%
  mutate(q_count= ifelse(count_q!=6, TRUE, FALSE)) %>%
  summarise(quint_error_total=sum(q_count,na.rm=TRUE))
#Text output when one or more sc quintile is missing from an NHS Board of Council Area
 ifelse(sc_quintile_warning $quint_error_total == 0, "No geogrpahies are missing a Scotland quintile",
 paste0("STOP and check table below!...There are ", sc_quintile_warning$quint_error_total[1]," geography/time periods where not all Scotland quintiles are present.  This is most likely in small areas eg Island regions.  If many regions are affected then indicator may not be suitable for publication."))       
# df to checkk how many areas are missing one or more scottish quintiles
sc_quintile_check <- data_indicator %>%
  subset(quint_type=="sc_quin") %>%
  mutate(q=paste0("Q",as.character(quintile))) %>%
  group_by(trend_axis, areaname, code,geo_type, q) %>%
  summarise(count=n())%>%
  spread(q, count) %>%
  mutate(qsum=sum(Q1,Q2,Q3,Q4,Q5,QTotal, na.rm=TRUE)) %>%
  ungroup() %>%
  subset(qsum<6) %>%
  arrange(geo_type,code, trend_axis)
# Flextable displying which geographies and years do not ahave all scotland quintiles represented
ft_sc_quintile_check <- sc_quintile_check %>%
  select(geo_type, areaname, code,trend_axis, Q1:qsum) %>%
  flextable() %>%
  bg(i= ~Q5==1, j= ~Q5, bg="red") %>%
  merge_v(j=c("areaname","code","geo_type")) %>%
  autofit() %>%
  theme_vanilla()
ft_sc_quintile_check
```

------------------------------------------------------------------------------------  

<!-- ##Data check 3: Compare previous file  -->
<!-- The table below compares the numerator, measure and CI of the latest file against the last shiny data file prepared.<br> -->
<!-- Conditional formatting will highlight when figures do not match, tolerance is to 3 decimal places <br> -->
<!-- Sometimes figures can change, e.g when the SMR records are more complete or new references files like the postcode lookups have been used.<br> -->
<!-- Use your judgement to decide if any differences are within acceptable range. -->

<!-- ```{r} -->
<!-- if(new_ind==FALSE){ -->
<!-- new_file <- data_indicator %>% subset(code %in% check_codes) -->
<!-- old_file <- old_data_indicator %>% subset(code %in% check_codes)%>% -->
<!--   select (code, year, quint_type,quintile, numerator, rate:rel_range) -->
<!-- #checks below only for matching rates/inequality estimates, not looking at CIs? -->
<!-- matched <- merge(x = new_file, y = old_file, by=c("code", "year","quint_type", "quintile")) %>% -->
<!--   mutate(rate_match = round((rate.x-rate.y)/rate.x,3), -->
<!--          sii_match = round((sii.x-sii.y)/sii.x,3), -->
<!--          rii_match = round((rii.x-rii.y)/rii.x,3), -->
<!--          par_match = round((par.x-par.y)/par.x,3), -->
<!--          year=as.factor(year), -->
<!--          sum_matches=sum(rate_match, sii_match, rii_match, par_match, na.rm=TRUE)) %>% -->
<!--   subset(sum_matches!=0) -->
<!-- if (nrow(matched) == 0) {"Old and new data files values match" -->
<!-- } else{ flextable(matched, -->
<!--   col_keys = c("code", "areaname","year","numerator.x", "numerator.y","numerator_match", -->
<!--                "rate.x", "rate.y","rate_match", -->
<!--                "sii.x","sii.y", "sii_match", -->
<!--                "rii.x","rii.y", "rii_match", -->
<!--                "par.x","par.y", "par_match")) %>% -->
<!--   set_header_labels(numerator.x="numerator_new", -->
<!--                     numerator.y="numerator_old", -->
<!--                     rate.x ="rate_new", -->
<!--                     rate.y="rate_old", -->
<!--                     sii.x="lowci_new", -->
<!--                     sii.y="lowci_old", -->
<!--                     rii.x="upci_new", -->
<!--                     rii.y="upci_old", -->
<!--                     par.x="upci_new", -->
<!--                     par.y="upci_old") %>% -->
<!--   autofit()} -->
<!-- }else if(new_ind==TRUE){ -->
<!--   "New_ind parameter set to TRUE - no historic checks run" -->
<!-- } -->
<!-- ``` -->

---------------------------------------------------------------------------------

##Data check 4:
####Rates within Confidence intervals
Do any rates fall outwith the confidence limits - they shouldn't!?

```{r, echo=FALSE}
# Check no rates/percentages sit outside of CI range  
 confidence_check <- data_indicator %>% 
  mutate(ci_error = ifelse(rate<lowci | rate>upci, TRUE, FALSE),
         sii_ci_error = ifelse(sii<lowci_sii | sii>upci_sii, TRUE, FALSE),
         rii_ci_error = ifelse(rii<lowci_rii | rii>upci_rii, TRUE, FALSE)) %>%
  summarise(ci_error_total = sum(ci_error,sii_ci_error,rii_ci_error, na.rm = TRUE))
ifelse(confidence_check$ci_error_total == 0, "No rates outwith confidence limits :-)",
"Uh-oh looks like there are some rates outwith confidence limits :(")
```

---------------------------------------------------------------------------------

##Data check 5:
#### Small numbers
Look at proportion of areas and quintiles where more than 10% of row include counts of less than 5 and therefore may not be robust. 

```{r}
small_count_data <- data_indicator  %>% 
  group_by(geo_type, quint_type, quintile, year) %>%
  summarise(count=n(),u5=sum(numerator<5)) %>%
  mutate(percent_U5=u5/count*100,
         year =as.factor(year)) %>%
  ungroup() %>%
  subset(percent_U5>10)
flextable(small_count_data)
```

-------------------------------------------------------------------------------

##Data check 6:
#### Check if there is a linear relationship across deprivation quintiles
This is a quick way to summarise if relationship with deprivation is clearly linear or not. If the relationship is obviously not linear then question whether measures such as SII and RII are helpful?

<!-- ```{r} -->
<!-- # look at which geographies codes/types have linear or non-linear patterns across deprivation quintiles  -->
<!-- linear_trends <- data_indicator  %>% -->
<!--   select(code, year, rate, quint_type, quintile, geo_type) %>% -->
<!--   subset(quintile != "Total") %>% -->
<!--   mutate(quintile=paste0("Q",quintile)) %>% -->
<!--   group_by(code, year, quint_type) %>% -->
<!--   spread(quintile, rate) %>% -->
<!--   mutate(pattern=case_when((Q1>Q2 & Q2>Q3 & Q3>Q4 & Q4>Q5)~"descending",(Q1<Q2 & Q2<Q3 & Q3<Q4 & Q4<Q5) ~"ascending", TRUE~"non_linear")) %>% -->
<!--   group_by(geo_type, quint_type, year, pattern) %>% -->
<!--   summarise(count=n()) %>% -->
<!--   group_by(geo_type, quint_type,year) %>% -->
<!--   mutate(sum=sum(count)) %>% -->
<!--   pivot_wider(names_from = pattern, values_from = count,values_fill=list(count=0)) %>% -->
<!--   mutate(percent_linear=100-round(non_linear/sum*100,1)) -->
<!-- ft <- linear_trends %>% -->
<!--  #select(geo_type,quint_type,year,ascending, descending, non_linear,sum,percent_linear) %>% -->
<!-- select_if(names(.) %in% c('geo_type','quint_type','year','ascending', 'descending','non_linear','sum','percent_linear')) %>% -->
<!--   flextable() %>% -->
<!--   merge_v(j=c("geo_type","quint_type")) %>% -->
<!--   autofit()%>% -->
<!--   theme_vanilla() -->
<!-- ft -->
<!-- ``` -->

-------------------------------------------------------------------------------
##Data check 7: Shiny app

```{r}
shinyApp(
  ui = fluidPage(
     fluidRow(
      fluidRow(column(12,(p("Use dropdowns to adjust charts - remember geography code selected needs to match the quintile type")))),
      column(5,selectInput("code_selected", "Area:", choices = unique(data_indicator$code_name),multiple = FALSE, selected="S00000001: Scotland")),
     column(3,selectInput("quint_selected", "Quintile:", choices = unique(data_indicator$quint_type),multiple = FALSE, selected="sc_quin")),
     column(3,selectInput("year_selected", "Year:", choices = unique(data_indicator$year),multiple = FALSE,selected=max(data_indicator$year)))),
     fluidRow(column(8,(h3("Check annual rates by quintile and rate trends")))),
     fluidRow(
       column(6,plotlyOutput("rate_bar")),
       column(6,plotlyOutput("rate_trend"))),
     fluidRow(column(8,(h3("Check SII and RII trends")))),
     fluidRow(
       column(6,plotlyOutput("sii_trend")),
       column(6,plotlyOutput("rii_trend"))),
     fluidRow(column(8,(h3("Check PAR")))),
     fluidRow(
       column(6,plotlyOutput("par_bar")),
       column(6,plotlyOutput("par_trend")))
    ),
  
  
  server = function(input, output) {
    
    #reactive simd trend data
    simd_trend_data<- reactive({
    rate_data <- data_indicator %>% # reactive dataset for trend chart
    select(code,code_name, year, numerator, denominator, rate, quint_type, quintile, geo_type, par, rii, sii) %>%
    subset(quint_type==input$quint_selected & code_name==input$code_selected) %>%
    arrange(quintile) %>% #this is needed to make palette assignments work well
    droplevels()
    })
    
    #reactive simd data single year
    simd_singleyr_data<- reactive({
    bar_rate_data <- simd_trend_data() %>% # reactive dataset for bar chart
     subset(year==input$year_selected) %>%
    mutate(average=rate[quintile=="Total"]) %>%
    filter(quintile !="Total") %>%
    droplevels()
    })
    
    # RATE-BAR CHART
    output$rate_bar <- renderPlotly({
    
    pal_rate_bar <- case_when(   simd_singleyr_data()$quintile == "1" ~ '#022031', #Palette for plot 
                                 simd_singleyr_data()$quintile == "2" ~ '#313695', 
                                 simd_singleyr_data()$quintile == "3" ~ '#4575b4', 
                                 simd_singleyr_data()$quintile == "4" ~ '#74add1', 
                                 simd_singleyr_data()$quintile == "5" ~ '#abd9e9')
    rate_bar <- plot_ly(data=   simd_singleyr_data(), x=~quintile) %>%
      #comparator line
     add_trace(y = ~average, name = "Average", type = 'scatter', mode = 'lines',
              line = list(color = '#FF0000'), hoverinfo="skip") %>%
      #quintile bars   
     add_bars(y = ~rate, color = ~ quintile, marker = list(color = pal_rate_bar))  %>%
      layout(title=paste0("Year: ",input$year_selected),bargap = 0.1, margin=list(b = 140),
             showlegend = FALSE) %>%
      config(displayModeBar = F, displaylogo = F, editable =F) # taking out toolbar
    })
    
    # RATE-LINE CHART
    output$rate_trend <- renderPlotly({
    
    #Palette for trend plot
    pal_simd_trend <- case_when(simd_trend_data()$quintile == "1" ~ '#022031',
                                    simd_trend_data()$quintile == "2" ~ '#313695',
                                    simd_trend_data()$quintile == "3" ~ '#4575b4',
                                    simd_trend_data()$quintile == "4" ~ '#74add1',
                                    simd_trend_data()$quintile == "5" ~ '#abd9e9',
                                    simd_trend_data()$quintile == "Total" ~ '#FF0000')
    tooltiptext_trend <- c(paste0(simd_trend_data()$year, ": ", simd_trend_data()$rate))
    
    #Create trend plot
    rate_trend <- plot_ly(data= simd_trend_data(), x=~year,hoverinfo="text") %>%
      add_lines(y = ~rate, name = ~quintile, type = 'scatter',text = tooltiptext_trend,
                mode = 'lines', color = ~quintile,  colors = pal_simd_trend)
    })
    
    # SII
    output$sii_trend <- renderPlotly({
      
    index_data <- simd_trend_data()  %>%  filter((quintile == "Total"))
    tooltiptext_sii <- c(paste0(index_data$year, ": ", index_data$sii))
    
    sii_trend <-plot_ly(data=index_data, x=~year, hoverinfo="text") %>%
          add_lines(y = ~sii, name = "Absolute inequality (SII)", type = 'scatter', 
                    text = tooltiptext_sii, mode = 'lines',
                    line = list(color = '#74add1'))  %>%
          config(displayModeBar = FALSE, displaylogo = F,  editable =F) # taking out toolbar
    })
    
    #RII
    output$rii_trend <- renderPlotly({
    index_data <- simd_trend_data()  %>%  filter((quintile == "Total"))
    tooltiptext_rii <- c(paste0(index_data$year, ": ", index_data$rii))
    
    plot_ly(data=index_data, x=~year,hoverinfo="text") %>%
          add_lines(y = ~rii, name = "Relative gap", type = 'scatter',
                    text = tooltiptext_rii, mode = 'lines',line = list(color = '#313695')) %>%
          config(displayModeBar = FALSE, displaylogo = F, editable =F) # taking out toolbar
    
    })
    
    
  #PAR Barchart
  output$par_bar <- renderPlotly({
    
  par_bar_data <- simd_singleyr_data() %>% 
       mutate(baseline = rate[quintile == "5"],
       diff_baseline = rate - rate[quintile == "5"]) %>% 
       droplevels()  
  plot_ly(data = par_bar_data, x = ~quintile,hoverinfo="text") %>%
      add_bars(y = ~baseline, name= "", marker = list(color = "#4da6ff"), showlegend = FALSE) %>%
      add_bars(y = ~diff_baseline, name = "Attributable to deprivation",
               marker = list(color = "#ffa64d"), showlegend = FALSE) %>%
      layout(title=paste0("Year: ",input$year_selected),
        bargap = 0.1, barmode = 'stack', showlegend = T,
             legend = list(x = 0.9, y = 0.9),
             margin = list(b = 140)) %>%
      config(displayModeBar = FALSE, displaylogo = F, editable =F) # taking out toolbar
  })
    #Par Trends  
output$par_trend <- renderPlotly({
  
  #preparing data needed
  simd_partrend_data <- simd_trend_data() %>%
    subset(quintile == "Total") %>% 
    droplevels()
  
  par_trend_plot <- plot_ly(data=simd_partrend_data, x=~year,
                              hoverinfo="text") %>%
      add_lines(y = ~par, type = 'scatter', mode = 'lines', line = list(color = "#4575b4")) %>%
      layout(margin = list(b = 140)) %>% #to avoid labels getting cut out
      config(displayModeBar = FALSE, displaylogo = F, editable =F) # taking out toolbar
    })
  
  
  
    },# server close
  options = list(height = 2000)
)
```

