---
title: "Data Quality Checks: Population Groups"
subtitle: "Report looks for errors in files intended for pop group tab of ScotPHO profiles tool"
output: html_document
runtime: shiny

---

```{r setup, include=FALSE}
#global options for markdown report
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}

rm(data_indicator)

# declare folder file path 
data_folder <- "/PHI_conf/ScotPHO/Profiles/Data/"

#read in geography code names dictionary
code_dictionary <-readRDS(paste0(data_folder,"Lookups/Geography/codedictionary.rds")) 

#Read in indicator file being checked (switch file path if working on test in
profiles_data_folder <- "/PHI_conf/ScotPHO/Profiles/Data"
output_folder <- if(test_file){
    file.path(profiles_data_folder, "Test Shiny Data") # for newly developed indicators that have never been in the profiles tool
    } else {
      file.path(profiles_data_folder, "Data to be checked") # for established indicators already in the profiles tool 
    }
  
#Read in indicator file being checked
data_indicator <- readRDS(paste0(output_folder,"/", filename, "_shiny_popgrp.rds")) %>%
  mutate(geo_type=substr(code,1,3)) #add field identifying geography type

#check if all expected columns for shiny tool are present & count number of columns present
columns_expected <-all(c("code","ind_id","year","numerator","rate","lowci","upci","def_period","trend_axis","split_value","split_name") %in% colnames(data_indicator))
column_count <- ncol(data_indicator)

#Add geography code names - useful when exploring outfiles in shiny
data_indicator <- left_join(x=data_indicator, y=code_dictionary, by="code") %>% 
mutate(code_name=paste0(code,": ",as.character(areaname)),#add field with geography code & name to ease identification
       geo_type=case_when(
          substr(data_indicator$code,1,3) == "S00" ~ "Scotland (S00)",
          substr(data_indicator$code,1,3) == "S08" ~ "NHS Board (S08)",
          substr(data_indicator$code,1,3) == "S12" ~ "Council (S12)",
          substr(data_indicator$code,1,3) == "S37" ~ "HSCP (S37)",
          substr(data_indicator$code,1,3) == "S11" ~ "ADP (S11)",
          substr(data_indicator$code,1,3) == "S99" ~ "HSCP Locality (S99)",
          substr(data_indicator$code,1,3) == "S32" ~ "Police Division (S32)",
          substr(data_indicator$code,1,3) == "S02" ~ "IZ (S02)",TRUE ~ "other")) 

#Logical test of which geographies are present in data set
# values will return TRUE/FALSE according to whether each geography type is present
board <- any(substr(data_indicator$code,1,3) == "S08") 
ca <- any(substr(data_indicator$code,1,3) == "S12")
hscp <- any(substr(data_indicator$code,1,3) == "S37")
adp <- any(substr(data_indicator$code,1,3) == "S11")
locality <- any(substr(data_indicator$code,1,3) == "S99")
iz <- any(substr(data_indicator$code,1,3) == "S02")
pd <- any(substr(data_indicator$code,1,3) == "S32")

#Read in old indicator data file from network /Shiny data folder - if one exists (new indicators won't have a historic file)
old_indicator_filepath <- paste0(data_folder, "Shiny Data/", filename, "_shiny_popgrp.rds") #create value which is file path to old file

# statement that checks if there an old indicator data file of the same name exists in Shiny data folder 
if(file.exists(old_indicator_filepath)) {
  skip_historic_file_checks <-"n" # if historic file found then instruct this report not to skip over thse checks
  old_data_indicator <- readRDS(paste0(data_folder, "Shiny Data/", filename, "_shiny_popgrp.rds")) #read in file if one exists
} else {
  skip_historic_file_checks <-"y" #if no historic file found then instruct this report to skip over some of the checks
  old_indicator_filepath <-"No historic file available for comparison. Check filename spelling or 'shiny data' network folder if you were expecting a comparison" #if no historic file exists set value to no file available
}

```


Indicator:  **`r filename`** <br>
Date:  **`r format(Sys.time(), '%d %B, %Y %H:%M')`** <br>

**New** indicator file:  /`r (paste0(output_folder,"/", filename, "_shiny_popgrp.rds"))`<br>
**Old** indicator file (for comparisons):  /`r (paste0(old_indicator_filepath)) `<br>

-----------------------------------------------------------------------------------

**Geographies present in indicator output file** <br>
NHS board: `r board` <br>
Council area: `r ca` <br>
Health and Social Care Partnership: `r hscp` <br>
Alcohol and Drugs Partnership: `r adp`<br>
HSC locality: `r locality`<br>
Intermediate zone: `r iz` <br>
Police division: `r pd` <br>

-----------------------------------------------------------------------------------
**Are expected columns present output file:**

```{r, out.width = "400px", echo=FALSE}

# paste warning if one or more column is missing from shiny data file
if (columns_expected == FALSE) {
    paste0("Shiny input file is missing required colummns")
} else {
    paste0("All expected columns present")
}
  
# paste warning if the column count isnt as expected (either too many or too few or missing expected)
if (column_count != 9 | columns_expected == FALSE) {
    paste0("Check columns in shiny input file - wrong column count or missing column")
} else {
    paste0("No extra columns")
}
```  

------------------------------------------------------------------------------------

###**Data check 1:**
<br>
####Which geographical levels and years are present & how many unique geographies appear?

```{r include=FALSE}
#Aggegrate file to detect which pop group splits for which geographies are present.
splits_present <-data_indicator %>%
  mutate(geo_type=substr(code,1,3)) %>%
  group_by(split_name, geo_type) %>%
  summarise(count=1) %>%
  spread(geo_type, count)

# ft_geo_check - summary table of years and geogrpahy types
# Conditional formatting on counts of geography types (except HSCP locality)
# Not sure how many localities there are supposed to be?
# Not sure how to handle indicators with ADP or only Council area - need to think about this...

ft_geo_check <- flextable(splits_present)


```  
Which population group splits are present in the data<br>
Still need to set up checks to specify which years for which geographies but this can be done later

```{r, out.width = "400px", echo=FALSE}

#print flextable
ft_geo_check %>%
  autofit()

```

------------------------------------------------------------------------------------  
###**Data check 2:**
<br>
####Rates & Confidence intervals
Do any rates fall outwith the confidence limits - they shouldn't!?

```{r, echo=FALSE}
# Check no rates/percentages sit outside of CI range  
 confidence_check <- data_indicator %>% 
  mutate(ci_error = ifelse(rate<lowci | rate>upci, TRUE, FALSE)) %>%
  summarise(ci_error_total = sum(ci_error, na.rm = TRUE))

```

```{r, echo=FALSE}
ifelse(confidence_check$ci_error_total == 0, "No rates outwith confidence limits :-)",
"Uh-oh looks like there are some rates outwith confidence limits :(")

```

---------------------------------------------------------------------------------
###**Data check 3:**
#### Small numbers
Look at proportion of areas and quintiles where more than 10% of row include counts of less than 5 and therefore may not be robust. 

```{r}
small_count_data <- data_indicator  %>% 
  group_by(geo_type,year,split_name, split_value) %>%
  summarise(count=n(),u5=sum(numerator<5)) %>%
  mutate(percent_U5=u5/count*100,
         year =as.factor(year)) %>%
  ungroup() %>%
  subset(percent_U5>10)

if(nrow(small_count_data)>0) {flextable(small_count_data)} else {"No counts less than 5."}


```

-------------------------------------------------------------------------------

###**Data check: Shiny app**
<br>
Shiny app to view data trends for one or more geography - some population gruop files only available at scotland level

```{r}

  shinyApp(

  ui = fluidPage(
    (p("Population groups indicator file checks")),
    selectInput("code_selected", "Area:", choices = unique(data_indicator$code_name),multiple = FALSE, selected="S00000001: Scotland"),
    selectInput("split_selected", "Split name:", choices = unique(data_indicator$split_name),multiple = FALSE),
    radioButtons("var_plot_trend", label =NULL, choices = c("Rate/Percentage"="rate", "Numerator"="numerator")),
    #radioButtons("ci_trend", label = "95% confidence intervals", choices = c("on","off"),selected = "off"), # ignore since not sure it works with multiple data series - conver to highcharter at some point?
    plotlyOutput("trend_plot")
    ),
  
  
  server = function(input, output) {
  
  # help prevent app crashing posit if the app fails  
  auto_invalidate <- reactiveTimer(10000) 
  observe({ auto_invalidate() 
  cat(".") 
  })

      #reactive simd trend data
    trend_data<- reactive({
    pgdata <- data_indicator %>% # reactive dataset for trend chart
    subset(split_name==input$split_selected & code_name %in% input$code_selected) %>%
    droplevels()
    })
  
      
         # Creating plot for ui side
  output$trend_plot <- renderPlotly({
    
    trend_palette <- c("#000000", "#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99",
                   "#e31a1c", "#fdbf6f", "#ff7f00", "#cab2d6", "#6a3d9a", "#b15928")
    
    #tool tip text for trend chart on population groups
    tooltiptext_trend <- c(paste0(trend_data()$trend_axis, ": ","<br>",
                              trend_data()$split_value,"<br>",
                              ": ",trend_data()$rate))
    
    #Create trend plot
    rate_trend <- plot_ly(data= trend_data(), x=~trend_axis, hoverinfo="text") %>%
      add_lines(y = ~get(input$var_plot_trend), name = ~split_value , type = 'scatter',
                text = tooltiptext_trend,mode = 'lines', color = ~split_value,  colors = trend_palette) %>%
      layout(yaxis = list(rangemode = "tozero")) # force yaxis to start at zero
  
    })
    
      },# server close
  
  options = list(height = 2000)
)
```

```{r, echo=FALSE}
# stop running shiny when close QA report
onStop(function() {
  stopApp()
})
```
