---
title: "ScotPHO Profile indicator Data Quality Checks"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}

##Libraries & set up (probably don't need to load these if data checks are incorporated to main indicator production script)**

library(foreign) #to read SPSS data.
library(dplyr) # for data manipulation
library(ggplot2) # for plotting
library(tidyr) # for data manipulation
library(RcppRoll) #for moving averages
library(readr) # writing csv's
library(odbc) # for reading oracle databases
library(readxl) #for reading excel
library(reshape2) # for dcasting/reshape
library(flextable) # for output tables
library(rmarkdown)
library(shiny)
library(plotly)

# Varies filepaths depending on if using server or not and what organisation uses it.
if (exists("organisation") == TRUE) { #Health Scotland
  if (organisation == "HS") { 
    data_folder <- "X:/ScotPHO Profiles/Data/" 
    lookups <- "X:/ScotPHO Profiles/Data/Lookups/"
  }
} else  { #ISD, first server then desktop
  if (sessionInfo()$platform %in% c("x86_64-redhat-linux-gnu (64-bit)", "x86_64-pc-linux-gnu (64-bit)")) {
    data_folder <- "/PHI_conf/ScotPHO/Profiles/Data/"
    lookups <- "/PHI_conf/ScotPHO/Profiles/Data/Lookups/" 
  } else {
    data_folder <- "//stats/ScotPHO/Profiles/Data/"
    lookups <- "//stats/ScotPHO/Profiles/Data/Lookups/" 
  }
}

#tokens that will be supplied by function
filename <- "breastfed"
IZ = TRUE  # Does indicator include IZ level data (#might need token for ADP or HSCP?)

check_codes =c("S00000001","S08000015","S12000010","S02001236") #user needs to input a selection of some gegraphies for checking


#Read in indicator file being checked
data_indicator <- readRDS(paste0(data_folder, "Data to be checked/", filename, "_shiny.rds")) 

#Reading last shiny data file loaded for comparisons.
# ?need error message if mathcing file name can't be found?

old_data_indicator <- readRDS(paste0(data_folder, "Shiny Data/", filename, "_shiny.rds")) 
```

Indicator:  **`r filename`**
<br>
Date:  **`r format(Sys.time(), '%d %B, %Y')`**
<br>

------------------------------------------------------------------------------------

**New** indicator file:  /`r (paste0(data_folder, "Data to be checked/", filename, "_shiny.rds"))`<br>
**Old** indicator file (for comparisons):  /`r (paste0(data_folder, "Shiny Data/", filename, "_shiny.rds"))`

------------------------------------------------------------------------------------

###Data check 1:
####What geotypes & years are present,how many unique geographies appear?

```{r, include=FALSE}
#Aggegrate file to detect which geographies and years are present.
geo_checks <- data_indicator %>%
  mutate(geo_type=substr(code,1,3)) %>%
  group_by(geo_type, trend_axis) %>%
  summarise(count=n()) %>%
  dcast(trend_axis ~ geo_type)

#ft_geo_check - summary table of years and geogrpahy types outputted - conditional formatting on counts
#no formatting set on hscp locality yet?

  if (IZ == TRUE) {
    ft_geo_check <- flextable(geo_checks) %>%
      color(~ S08!=14, ~S08, color = "red") %>% #NHS board should be 14
      color(~ S12!=32, ~S12, color = "red") %>% #S12 council should be 32
      color(~ S37!=31, ~S37, color = "red") %>% #HSCP should be 31
      color(~ S02!=1279,~S02, color = "red") %>% #There should be 1279 IZ
      autofit()
  } else if (IZ==FALSE) {
     ft_geo_check <- flextable(geo_checks) %>%
       color(~ S08!=14, ~S08, color = "red") %>% #NHS board should be 14
       color(~ S12!=32, ~S12, color = "red") %>% #S12 council should be 32
       color(~ S37!=31, ~S37, color = "red") %>%  #HSCP should be 31
       autofit()
  }
```  

Are the expected geographies appearing for all expected years?<br>
Cells contain the number of unique geography codes split by geography type.<br>
Conditional formatting highlights where geographies present are not equal to expected (e.g. 14 NHS boards, 32 councils or 31 HSCP)<br>
If some geographies are missing consider:<br>
Is any suppression already applied to the dataset?<br>
Might there legitimately be no data for that area (e.g. there might have been no deaths in that intermediate zone)?

```{r, echo=FALSE}
#print flextable
ft_geo_check 

```
------------------------------------------------------------------------------------  


###Data check 2:
####How many new rows added in latest update?

```{r, include=FALSE}
new_row <- nrow(data_indicator)
old_row <- nrow(old_data_indicator)

```

1.Rows in new shiny file: **`r new_row`** <br>
2.Rows added compared to last file: **`r paste0(c(new_row-old_row))`**

------------------------------------------------------------------------------------  

###Data check 3:
####How does new data compare to figures live profile data?

```{r, include=FALSE}
new_Scot <-data_indicator %>% subset(code %in% check_codes)
old_Scot <- old_data_indicator %>% subset(code %in% check_codes)%>%
  select (code, year, numerator, rate, lowci, upci)

#calculate percentage difference between old and new figures
matched <- merge(x = new_Scot, y = old_Scot, by=c("code", "year")) %>%
  mutate(numerator_match =  (numerator.x - numerator.y)/numerator.x,
         rate_match = (rate.x-rate.y)/rate.x,
         lowci_match = (lowci.x-lowci.y)/lowci.x,
         upci_match = (upci.x-upci.y)/upci.x)

```
The table below compares the numerator, measure and CI of latest file against those in the live shiny data file. <br>
Conditional formatting will highlight when figures do not match, tolerance is zero so any difference will be highlighted. <br>
Sometimes figures can change, maybe the SMR records are more complete or new references files like the postcode lookup have been used which make small differences.Use your judgement to decide if any differences are acceptable.

```{r, echo=FALSE}
flextable(matched,
  col_keys = c("code","year","numerator.x", "numerator.y","numerator_match",
               "rate.x", "rate.y","rate_match",
               "lowci.x","lowci.y", "lowci_match",
               "upci.x","upci.y","upci_match")) %>%
  set_header_labels(numerator.x="numerator_new",
                    numerator.y="numerator_old",
                    rate.x ="rate_new",
                    rate.y="rate_old",
                    lowci.x="lowci_new",
                    lowci.y="lowci_old",
                    upci.x="upci_new",
                    upci.y="upci_old") %>%
  color(~ numerator_match !=0,~numerator_match, color = "red") %>% #
  color(~ rate_match !=0,~rate_match, color = "red") %>% 
  color(~ lowci_match !=0,~lowci_match, color= "red") %>% 
  color(~ upci_match !=0,~upci_match, color = "red") %>%
  autofit()
```

####Data check 4:
####Scotland & NHS boards?

```{r, include=FALSE}
scot_value <-data_indicator %>% filter((code=="S00000001")& year==max(year)) %>%select(rate)

#Selecting Health boards and Scotland for latest year in dataset
scot_check <- ggplot(data = data_indicator %>% filter((substr(code, 1, 3)=="S08" | code=="S00000001") 
                                        & year== max(year)), aes(code, rate) ) +
  geom_point(stat = "identity") +
  geom_hline(yintercept= scot_value$rate[1], linetype="dashed", color = "red")+
  geom_errorbar(aes(ymax=upci, ymin=lowci), width=0.5)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 

```
Does Scotland rate seem like a sensible figure, how wide are the confidence intervals? <br>
Does Scotland rate look about average of all NHS boards.<br>
Are there any outliers or strange looking confidence intervals (expect Island boards to have wide CI)

```{r, echo=FALSE}
scot_check
```

------------------------------------------------------------------------------------  
###Data check 5:
####Are geographies that ought to be the same matching?


```{r, include=FALSE}

#Selecting Council area, HSCP and its localities for latest year in dataset
#test case#1
#city of edinburgh council = S1200036
#city of edinburgh partnership = S37000012
#Edinburgh localities = S99000044,45,46,47

edinburgh_data <- data_indicator %>% 
  filter(code =="S12000036" | code=="S37000012"|code=="S99000044"|code=="S99000045"|code=="S99000046"|code=="S99000047") %>%
  mutate(geotype=substr(code,1,3)) %>%
  group_by(year, geotype) %>%
  summarise(numerator=sum(numerator)) %>%
  dcast(year ~ geotype) %>%
  mutate(ca_partnership=round(S12-S37,2),
         partnership_localities=round(S99-S37,2),
         localities_ca=round(S99-S12,2),
         check_tot=sum(ca_partnership,partnership_localities,localities_ca))

# ft_edinburgh_check <- flextable(edinburgh_data) %>%
#   color(~ check_tot!=0, ~check_tot, color = "red") %>%
#   color(~ ca_partnership!=0, ~ca_partnership, color = "red") %>%
#   color(~ partnership_localities!=0, ~partnership_localities, color = "red") %>%
#   color(~ localities_ca!=0, ~localities_ca, color = "red") %>%
#   autofit()


edinburgh_chart <- ggplot(data = data_indicator %>% 
         filter((code =="S12000036" | code=="S37000012"
                |code=="S99000044"|code=="S99000045"|code=="S99000046"|code=="S99000047") & year== max(year)), aes(code, rate)) +
  geom_point(stat = "identity") +
  geom_errorbar(aes(ymax=upci, ymin=lowci), width=0.5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

```{r, echo=FALSE}
if(sum(edinburgh_data$check_tot==0)){"Cool...Numerators for Edinburgh council, HSCP and localitys all agree :-)"}

if(sum(edinburgh_data$check_tot!=0))
{flextable(edinburgh_data) %>%
  add_header_lines("uh-oh.  Doesn't look like the numerators for Edinburgh localities, hscp &/or council areas tally") %>%
    fontsize(part = "header", size = 16) %>%
  color(~ check_tot!=0, ~check_tot, color = "red") %>%
  color(~ ca_partnership!=0, ~ca_partnership, color = "red") %>%
  color(~ partnership_localities!=0, ~partnership_localities, color = "red") %>%
  color(~ localities_ca!=0, ~localities_ca, color = "red") %>%
  autofit()  }

```

------------------------------------------------------------------------------------  
###Data check 6:
Small shiny app to view data trends for one or more geography

```{r, echo=FALSE}
shinyApp(

  ui = fluidPage(
     selectInput("code_selected", "Area:", choices = unique(data_indicator$code),multiple = TRUE, selected="S00000001"),
     radioButtons("var_plot_trend", label =NULL, 
                                       choices = c("Rate/Percentage"="rate", 
                                                   "Numerator"="numerator")),
    plotlyOutput("trend_plot")
    ),

  server = function(input, output) {
    
    trend_data <- reactive({ 
         data <- data_indicator %>%
           subset(code %in% input$code_selected)
      })


    plot_trend_chart <- function() {
    
    #Text for tooltip
    tooltip_trend <- c(paste0(trend_data()$code, "<br>",
                              "Rate: ", round(trend_data()$rate,2), "<br>",
                              "Numerator: ", round(trend_data()$numerator, 1)))

    trend_plot <- plot_ly(data=trend_data(), x=~trend_axis,  y = ~get(input$var_plot_trend),
                          text=tooltip_trend, height = 600) %>% 
        add_trace(type = 'scatter', mode = 'lines+markers',symbol = ~trend_data()$code) %>% 
        #Layout 
        layout(annotations = list(), #It needs this because of a buggy behaviour of Plotly
               yaxis = list(title = input$var_plot_trend, rangemode="tozero", fixedrange=TRUE,
                            size = 4, titlefont =list(size=14), tickfont =list(size=14)),
               xaxis = list(title = FALSE, tickfont =list(size=14), tickangle = 270, fixedrange=TRUE),
               showlegend = TRUE,
               legend = list(orientation = 'h', x = 0, y = 1.18)) %>%  #legend on top
        config(displayModeBar = FALSE, displaylogo = F) # taking out plotly logo button
      
    }
    
      # Creating plot for ui side
  output$trend_plot <- renderPlotly({ plot_trend_chart()
    }) 
    

    },# server close
  options = list(height = 800)
)
```
------------------------------------------------------------------------------------  
###Data check 7:
####Are numerator likely to generate a robust indicator?

The table below allows you to assess by geogrpahy type & year how many rows contain cell with numerator is <5 or <10.  There is not definte point at which an indicator is no loger robust but if a large prorotion of your data is small numbers then consider whether the data is worth publishing.


```{r, include=FALSE}
small_count_data <- data_indicator  %>% 
  mutate(geo_type=substr(code,1,3)) %>%
  group_by(geo_type, year) %>%
  summarise(count=n(),
            u5=sum(numerator<5),
            u10=sum(numerator<10)) %>%
  mutate(percent_U5=u5/count*100,
         percent_U10=u10/count*100) %>%
  subset(percent_U5>0)

```

```{r, echo=FALSE}
flextable(small_count_data)
```


<br>
<br>
End of checks....Hurray!
