---
title: "ScotPHO Profiles QA report - in development"
#subtitle: "School leavers in positive destinations"
author: "Andy Pulford"
date: '`r format(Sys.Date(), "%d %B %Y")`'
params:
  id: 13012
  name: school_meals
output: 
  html_document:
    code_folding: hide
---

```{r, message=FALSE, warning=FALSE}
# packages
#library(googlesheets) # work out how to load straight from google docs
library(tidyverse)

# load technical document
tech <- read_csv("./Technical Document - Raw.csv") %>% 
  filter(indicator_number == params$id) # copy from title

# load or link to raw data = to be added ----------------------------------

# load indicator data
data <- read_csv(paste0("X:/ScotPHO Profiles/Data/Data to be checked/",params$name,"_shiny.csv"))

# define variable names as they should appear in OPT file
sop_names <- c("code", "year", "numerator", "denominator", 
               "rate", "lowci", "upci", "ind_id", "trend_axis", "def_period" )

# create dataframe to summarise missing vars
na <- sapply(data, function(x) sum(is.na(x)))
na <- data.frame(sop_names, na) %>% as_tibble() %>% 
  rename(
    var = sop_names,
    missing = na
  )

# create dataframe to check numerators add up to higher geogs
sc_num <- data %>% filter(code == "S00000001") %>% 
group_by(year) %>% 
  summarise(sc = sum(numerator, na.rm = TRUE)) %>% 
  ungroup()

hb_num <- data %>% filter(substr(code, 1, 3) == "S08")%>% 
  group_by(year) %>% 
  summarise(hb = sum(numerator, na.rm = TRUE))%>% 
  ungroup()

la_num <- data %>% filter(substr(code, 1, 3) == "S12")%>% 
  group_by(year) %>% 
  summarise(la = sum(numerator, na.rm = TRUE))%>% 
  ungroup()

num_check <- sc_num %>% full_join(by = "year", hb_num)
num_check <- num_check %>% full_join(by = "year", la_num)

```

#Profile details
**Indictaor name:** `r tech$indicator_name`  
**Indicator ID:** `r tech$indicator_number`  
**Profile:** `r tech$profile`  
**Indicator type:**	`r tech$measure`  
**Year type:**	`r tech$year_type`  
**Aggregation:** `r tech$aggregation`  
**Trend period:** `r tech$trends_from`  
**Geographies:** `r tech$available_geographies`  

#Check OPT file
* Data `r ifelse(sum(names(data) == sop_names) == 10, "", "**do not** ")` match the format in the SOP.  
* The indicator ID  `r ifelse(first(data$ind_id) == tech$indicator_number, "matches", "**does not match**")` the technical document.  
* Compare year type in OPT file against technical document:
    + **`r first(data$def_period)`** vs. **`r tech$year_type`**  
* The current published time trend is for **`r tech$trends_from`**:
    + Start year in data: `r min(data$year)`
    + End year in data: `r max(data$year)`
* Aggregation is by `r tech$aggregation`
* Check for missing fields:  
`r knitr::kable(na[,1:2])`
* Check aggregation of numerators up to higher geographies:  
`r knitr::kable(num_check)`

```{r, message=FALSE, warning=FALSE}
# create df for checking that LAs aggregate to HBs
aa_hb <- data %>% filter(code == "S08000015") %>% 
  select(year, code, numerator)
  
aa_la <- data %>% filter(code %in% c("S12000008",
                            "S12000021",
                            "S12000028")) %>% 
  group_by(year) %>% 
  summarise(hb = sum(numerator, na.rm = TRUE)) %>% 
  ungroup()

aa_check <- aa_hb %>% full_join(by = "year", aa_la)


```
* Check LA to HB aggregation:
`r knitr::kable(aa_check)`

* rate/percantage calculation check - manual against raw data?  
* Minimum and maximum CI ranges:  
    + Min: `r data %>% mutate(ci_range = upci-lowci) %>% 
    summarise(min_ci_range = min(ci_range, na.rm = TRUE))`  
    + Max: `r data %>% mutate(ci_range = upci-lowci) %>% 
    summarise(min_ci_range = max(ci_range, na.rm = TRUE))`
* Check no rates/percentages sit outside of CI range  
    + `r  data %>% mutate(ci_error = ifelse(rate<lowci | rate>upci, TRUE, FALSE)) %>% 
                  summarise(ci_error_totoal = sum(ci_error, na.rm = TRUE))` rows with rate outside of CI range
* Compare Scotland to median LA or HB rate/percentage  
* Plot chart as per analysis script:  
```{r, echo = TRUE, message=FALSE, warning=FALSE}   
#Selecting Health boards and Scotland for latest year in dataset
    ggplot(data = data %>% filter((substr(code, 1, 3)=="S08" | code=="S00000001") 
                                              & year== max(year)), aes(code, rate) ) +
      geom_point(stat = "identity") +
      geom_errorbar(aes(ymax=upci, ymin=lowci), width=0.5) + 
  theme(axis.text.x = element_text(angle = 90)) 
```

#First person QA notes  
<add here>  

#Second person QA notes  
<add here>  

```{r}
## create indictaor specific hmtl doc
render_name <- eval(paste0(params$id,"_",params$name,"_qa.html"))
rend_doc <- function(render_name) {
  rmarkdown::render("qa_report.Rmd", 
                  output_file = render_name)
}
```
